\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference}

### 2021-09-24 paper/r1/manuscript-mssp.tex
reponse to reviwer 2

		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{}
		%% \address[label1]{}
		%% \address[label2]{}
		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	To evaluate the performance of single base station \textcolor{r_s}{real-time} kinematic(RTK) and network \textcolor{r_s}{real-time} kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	\textcolor{r_s}{
		Moschas et al.\cite{Moschas_2014} studied the extraction of strong motion displacement waveform by PPP and evaluated it through free vibration experiments. These results show that 10 Hz PPP-GPS is very useful for seismic engineering and can be safely used to reconstruct the deflection waveforms of various points on the ground and structure during strong motion.}
	\textcolor{r_s}{Zhang et al.\cite{Meng_2019} introduced Galileo augmenting GPS single-frequency single-epoch precise positioning method with baseline constrain for bridge dynamic monitoring, to improve the positioning availability and reliability, as well as narrow the search space, and increase the success rate of ambiguity resolution and positioning.
	Xue et al.\cite{Xue2021} comprehensively evaluated multi-GNSS low-cost receivers for deformation monitoring and concluded that the potential improvement of the precision of the low-cost receiver by using multi-GNSS measurements and a GNSS base station with a geodetic antenna.}
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	\textcolor{r_s}{
	The other category is displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement \textcolor{r_s}{for} 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month field monitoring provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test and the control network processing results are generally based on repeated static adjustment.
	}

@@

	\section{Methodology}
	\label{method}
	\textcolor{r_s}{A displacement detection method for deformation monitoring is proposed, which detects displacement, thus probably landslide, subsidence behavior. The method mainly includes three steps: GNSS kinematic positioning, Bayesian inference, and posterior sample analysis. The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.}
	\begin{figure*}[htpb]
		\centering
		\includegraphics[scale=0.45]{v_workflow}
		\caption{\textcolor{r_s}{Displacement detection method based on Bayesian inference.}}
		\label{fig_v_workflow}
	\end{figure*}

@@

	As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.
	\textcolor{r_s}{
		This is the first time that Bayesian inference has been used for displacement detection based on GNSS kinematic positioning.
		Compared with indicator-based detection methods, this method has high robustness and flexibility.
		The method based on Bayesian inference uses multi-epoch observation data, which is more reliable.
		On the other hand, the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori. Although only the vertical direction has been verified due to the experimental equipment, the horizontal direction should also be adapted because the vertical direction is noisier.
	}

>>>>

		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference}}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{}
		%% \address[label1]{}
		%% \address[label2]{}
		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	To evaluate the performance of single base station \textcolor{r_s}{real-time} kinematic (RTK) and network \textcolor{r_s}{real-time} kinematic (NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position (PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	\textcolor{r_s}{
		Moschas et al.\cite{Moschas_2014} studied the extraction of strong motion displacement waveform by PPP and evaluated it through free vibration experiments. These results show that 10 Hz PPP-GPS is very useful for seismic engineering and can be safely used to reconstruct the deflection waveforms of various points on the ground and structure during strong motion.}
	\textcolor{r_s}{Zhang et al.\cite{Meng_2019} introduced Galileo augmenting GPS single-frequency single-epoch precise positioning method with baseline constrain for bridge dynamic monitoring, to improve the positioning availability and reliability, as well as narrow the search space, and increase the success rate of ambiguity resolution and positioning.
	Xue et al.\cite{Xue2021} comprehensively evaluated multi-GNSS low-cost receivers for deformation monitoring and concluded that the potential improvement of the precision of the low-cost receiver by using multi-GNSS measurements and a GNSS base station with a geodetic antenna.}
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	\textcolor{r_s}{
	The other category is displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop (PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement \textcolor{r_s}{for} 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month field monitoring provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test and the control network processing results are generally based on repeated static adjustment.
	}

@@

	\section{Methodology}
	\label{method}
	\textcolor{r_s}{A displacement detection method for deformation monitoring is proposed, which detects displacement, thus probably landslide, subsidence behavior. The method mainly includes three steps: GNSS kinematic positioning, Bayesian inference, and posterior sample analysis. The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.}
	\begin{figure*}[htpb]
		\centering
		\includegraphics[scale=0.45]{v_workflow}
		\caption{\textcolor{r_s}{Displacement detection based on Bayesian inference from GNSS Kinematic Positioning.}}
		\label{fig_v_workflow}
	\end{figure*}

@@

	As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.
	\textcolor{r_s}{
		This is the first time that Bayesian inference has been used for displacement detection from GNSS kinematic positioning.
		Compared with indicator-based detection methods, this method has high robustness and flexibility.
		The method based on Bayesian inference uses multi-epoch observation data, which is more reliable.
		On the other hand, the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori. Although only the vertical direction has been verified due to the experimental equipment, the horizontal direction should also be adapted because the vertical direction is noisier.
	}
